Weighted Averaging of Multiple Non-collocated Inertial Measurement Units

### 2024-08-28 paper/main.tex
Addressed how we do propagation with raw measurement and estimated biases.
Added a recap for VIMU method.

@@

\begin{equation}
    \textbf{y}_{\omega,i}(t) = \textbf{C}_{i}^{-1} \bm{\omega}(t) + \textbf{b}_{\omega, i}(t) + \textbf{n}_{\omega,i}(t)
\end{equation}
\begin{equation}
\begin{split}
    \textbf{y}_{a,i}(t) &= \textbf{C}_i^{-1} \left[ \textbf{a}(t) + \bm{\omega}(t)^\wedge (\bm{\omega}(t)^\wedge \textbf{r}_i) + \bm{\alpha}(t)^\wedge \textbf{r}_i \right] \\
    &+ \textbf{b}_{a,i}(t) + \textbf{n}_{a,i}(t) + \textbf{C}_i^{-1} \textbf{C}^{-1}(t) \textbf{g}
\end{split}
\end{equation}

@@

\textcolor{red}{Talk about propagtion step}

@@

First we align each IMU measurement with vehicle frame.
\begin{equation}
    \textbf{C}_{i} \textbf{y}_{\omega,i}(t) = \bm{\omega}(t) + \textbf{C}_{i} \textbf{b}_{\omega, i}(t) + \textbf{C}_{i} \textbf{n}_{\omega,i}(t)
\end{equation}
\begin{equation}\label{eqn_accel}
\begin{split}
    \textbf{C}_{i} \textbf{y}_{a,i}(t) &= \textbf{a}(t) + \bm{\omega}(t)^\wedge (\bm{\omega}(t)^\wedge \textbf{r}_i) + \bm{\alpha}(t)^\wedge \textbf{r}_i \\
    &+ \textbf{C}_{i} \textbf{b}_{a,i}(t) + \textbf{C}_{i} \textbf{n}_{a,i}(t) + \textbf{C}^{-1}(t)\textbf{g}
\end{split}
\end{equation}

For gyroscope measurement, the weighted average ($\sum_i{a_i} = 1$) of all IMU measurement is simply,
\begin{equation}
\begin{split}
    \bar{\textbf{y}}_\omega(t) &= \sum_i{a_i \textbf{C}_{i} \textbf{y}_\omega(t)} \\
    &= \sum_i{a_i \left( \bm{\omega}(t) + \textbf{C}_{i} \textbf{b}_{\omega,i}(t) + \textbf{C}_{i} \textbf{n}_{\omega,i}(t) \right)} \\
    &= \bm{\omega}(t) + \sum_i{a_i \textbf{C}_{i} \textbf{b}_{\omega,i}(t)} + \sum_i{a_i \textbf{C}_{i} \textbf{n}_{\omega,i}(t)}
\end{split}
\end{equation}

@@

Since all biases are slow varying we can estimate the combined bias drift instead of the individual ones.

@@

Summing equation \ref{eqn_accel} of all accelerometers we have,
\begin{equation}
\begin{split}
    \bar{\textbf{y}}_a(t) &= \sum_i{a_i \textbf{C}_{i} \textbf{y}_a(t)} \\
    &= \textbf{a}(t) + \textbf{C}^{-1}(t)\textbf{g} \\
    &+ \sum_i{a_i \bm{\omega}(t)^\wedge (\bm{\omega}(t)^\wedge \textbf{r}_i)} + \sum_i{a_i \bm{\alpha}(t)^\wedge \textbf{r}_i} \\
    &+ \sum_i{a_i \textbf{C}_{i} \textbf{b}_{a,i}(t)} + \sum_i{a_i \textbf{C}_{i} \textbf{n}_{a,i}(t)}
\end{split}
\end{equation}

Using the associate rule $\textbf{a}^\wedge \textbf{b} + \textbf{a}^\wedge \textbf{c} = \textbf{a}^\wedge \left(\textbf{b} + \textbf{c}\right)$, we have,
\begin{equation}
\begin{split}
    \bar{\textbf{y}}_a(t) &= \sum_i{a_i \textbf{C}_{i} \textbf{y}_a(t)} \\
    &= \textbf{a}(t) + \textbf{C}^{-1}(t)\textbf{g} \\
    &+ \bm{\omega}(t)^\wedge \left(\bm{\omega}(t)^\wedge \left( \sum_i{a_i \textbf{r}_i} \right) \right) + \bm{\alpha}(t)^\wedge \left( \sum_i{a_i\textbf{r}_i} \right)\\
    &+ \sum_i{a_i \textbf{C}_{i} \textbf{b}_{a,i}(t)} + \sum_i{a_i \textbf{C}_{i} \textbf{n}_{a,i}(t)}
\end{split}
\end{equation}

If $\sum_i{a_i \textbf{r}_i} = \textbf{0}$ then we eliminate the terms due to lever arm effect. This gives,
\begin{equation}
    \bar{\textbf{y}}_a(t) = \textbf{a}(t) + \textbf{C}(t)\textbf{g} + \bar{\textbf{b}}_a(t) + \bar{\textbf{n}}_a(t)
\end{equation}

@@

Summarize the simplified IMU model from averaging multiple IMUs with separation.

\textcolor{red}{Talk about the combined bias drift rate and noise variance.}

@@

\textcolor{red}{need to include the noise term in the derivation for solution}

@@

What we did. What is the benefit. \cite{Farahan2022}.

>>>>

Due to the presence of biases, it is estimated as part of the state vector and subtracted from the raw measurement to get the unbiased measurement for propagation.
\begin{equation}
\begin{split}
    \hat{\bm{\omega}}(t) = \textbf{y}_\omega(t) - \hat{\textbf{b}}_\omega(t) \\
    \hat{\textbf{a}}(t)  = \textbf{y}_a(t) - \hat{\textbf{b}}_a(t)
\end{split}
\end{equation}

@@

\begin{equation}
    \textbf{y}_{\omega,i}(t) = \textbf{C}_{i}^{-1} \bm{\omega}(t) + \textbf{b}_{\omega, i}(t) + \textbf{n}_{\omega,i}(t)
\end{equation}
\begin{equation}
\begin{split}
    \textbf{y}_{a,i}(t) &= \textbf{C}_i^{-1} \left[ \textbf{a}(t) + \bm{\omega}(t)^\wedge (\bm{\omega}(t)^\wedge \textbf{r}_i) + \bm{\alpha}(t)^\wedge \textbf{r}_i \right] \\
    &+ \textbf{b}_{a,i}(t) + \textbf{n}_{a,i}(t)
\end{split}
\end{equation}

@@

@@

First we align gyroscope measurement with vehicle frame.
\begin{equation}
    \textbf{C}_{i} \textbf{y}_{\omega,i}(t) = \bm{\omega}(t) + \textbf{C}_{i} \textbf{b}_{\omega, i}(t) + \textbf{C}_{i} \textbf{n}_{\omega,i}(t)
\end{equation}

The weighted average ($\sum_i{a_i} = 1$) of all gyroscope is simply,
\begin{equation}
\begin{split}
    \bar{\textbf{y}}_\omega(t) &= \sum_i{a_i \textbf{C}_{i} \textbf{y}_\omega(t)} \\
    &= \sum_i{a_i \left( \bm{\omega}(t) + \textbf{C}_{i} \textbf{b}_{\omega,i}(t) + \textbf{C}_{i} \textbf{n}_{\omega,i}(t) \right)} \\
    &= \bm{\omega}(t) + \sum_i{a_i \textbf{C}_{i} \textbf{b}_{\omega,i}(t)} + \sum_i{a_i \textbf{C}_{i} \textbf{n}_{\omega,i}(t)}
\end{split}
\end{equation}

@@

@@

Align the all accelerometer measurement to vehicle frame.
\begin{equation}\label{eqn_accel}
\begin{split}
    \textbf{C}_{i} \textbf{y}_{a,i}(t) &= \textbf{a}(t) + \bm{\omega}(t)^\wedge (\bm{\omega}(t)^\wedge \textbf{r}_i) + \bm{\alpha}(t)^\wedge \textbf{r}_i \\
    &+ \textbf{C}_{i} \textbf{b}_{a,i}(t) + \textbf{C}_{i} \textbf{n}_{a,i}(t)
\end{split}
\end{equation}

Summing equation \ref{eqn_accel} of all accelerometers we have,
\begin{equation}
\begin{split}
    \bar{\textbf{y}}_a(t) &= \sum_i{a_i \textbf{C}_{i} \textbf{y}_a(t)} \\
    &= \textbf{a}(t) + \sum_i{a_i \textbf{C}_{i} \textbf{b}_{a,i}(t)} + \sum_i{a_i \textbf{C}_{i} \textbf{n}_{a,i}(t)} \\
    &+ \sum_i{a_i \bm{\omega}(t)^\wedge (\bm{\omega}(t)^\wedge \textbf{r}_i)} + \sum_i{a_i \bm{\alpha}(t)^\wedge \textbf{r}_i} \\
\end{split}
\end{equation}

Using the associate rule $\textbf{a}^\wedge \textbf{b} + \textbf{a}^\wedge \textbf{c} = \textbf{a}^\wedge \left(\textbf{b} + \textbf{c}\right)$, we have,
\begin{equation}
\begin{split}
    \bar{\textbf{y}}_a(t) &= \sum_i{a_i \textbf{C}_{i} \textbf{y}_a(t)} \\
    &= \textbf{a}(t) + \sum_i{a_i \textbf{C}_{i} \textbf{b}_{a,i}(t)} + \sum_i{a_i \textbf{C}_{i} \textbf{n}_{a,i}(t)} \\
    &+ \bm{\omega}(t)^\wedge \left(\bm{\omega}(t)^\wedge \left( \sum_i{a_i \textbf{r}_i} \right) \right) + \bm{\alpha}(t)^\wedge \left( \sum_i{a_i\textbf{r}_i} \right)\\
\end{split}
\end{equation}

If $\sum_i{a_i \textbf{r}_i} = \textbf{0}$ then we eliminate the last two terms from lever arm effect. This gives,
\begin{equation}
    \bar{\textbf{y}}_a(t) = \textbf{a}(t) + \bar{\textbf{b}}_a(t) + \bar{\textbf{n}}_a(t)
\end{equation}

@@

Since all biases are slow varying, the combined biases are also slow varying. So instead of tracking individual biases, only the combined biases are needed. When receiving new set of IMU measurement, we estimate the angular velocity and linear acceleration with the update equations below.
\begin{equation}
\begin{split}
    \hat{\bm{\omega}}(t) = \bar{\textbf{y}}_\omega(t) - \hat{\bar{\textbf{b}}}_\omega(t) \\
    \hat{\textbf{a}}(t)  = \bar{\textbf{y}}_a(t) - \hat{\bar{\textbf{b}}}_a(t)
\end{split}
\end{equation}

The combined measurement is expected to have slower drift and the estimate is expected to be less noisy as well \cite{patel2022_multi-imu}. If having $n$ identical IMUs and equal weight the standard deviation of the combined noise or drift rate is expected to be,
\begin{equation}
    \bar{\sigma} = \frac{\sigma}{\sqrt{n}}
\end{equation}

@@

@@

What we did. What is the benefit.
